### 2022-12-15 abstract.tex
rewrite intro and abstract a bit

% The credibility of a scientific finding is based on the fact that it can be
% replicated when the same study is repeated with new subjects.
An important aspect for the credibility of a scientific finding is that the
finding can be replicated when the same study is repeated with new subjects.
However, various failures to replicate major scientific findings in the social
and life sciences indicate that replicability is often lower than expected. This
``replication crisis'' has led to several methodological reforms in the past
decade, an increased conduct of replication studies being one of them. Yet
despite this increase in replication studies, there is no consensus on a
fundamental question: How should replication success be defined statistically?
% Various methods already exist and various new ones have been proposed in
% response to the crisis. This thesis centres around a proposal based on the
% reverse-Bayes approach. The key idea is to reverse the traditional ``forward''
% use of Bayes' theorem (``prior + likelihood $\rightarrow$ posterior''),
% starting instead with a pre-specified posterior and deducing the corresponding
% prior (``posterior + likelihood $\rightarrow$
% prior''). % As such, the reverse-Bayes approach naturally fits to the replication
% % setting as it enables the mathematical formalization of scepticism regarding the
% % finding from the original study.
% This allows us to challenge the original finding by determining a sceptical
% prior for the underlying effect size such that the resulting posterior is no
% longer convincing. This prior then represents the position of a sceptic who
% remains unconvinced by the original study. Whether or not the sceptics'
% position is justified can then be assessed in light of the new data from the
% replication study. The larger the conflict between the replication data and
% the sceptic, the larger the degree of replication success. This procedure can
% be summarized in a single quantitative measure of replication success, termed
% the sceptical $p$-value.

>>>>

% The credibility of a scientific finding is based on the fact that it can be
% replicated when the same study is repeated with new subjects.
% An important aspect of the credibility of a scientific finding is that the
% finding can be replicated when the same study is repeated with new subjects.
% An important aspect of the credibility of a scientific finding is its
% replicability -- the ability to produce similar results when the same study is
% repeated with new subjects.
An important aspect of the credibility of a scientific finding is its
replicability -- the ability that a similar finding can be obtained when the
same study is repeated with new subjects. However, various failures to replicate
major scientific findings in the social and life sciences indicate that
replicability is often lower than expected. This ``replication crisis'' has led
to several methodological reforms in the past decade, an increased conduct of
replication studies being one of them. Yet despite this increase in replication
studies, there is no consensus on a fundamental question: How should replication
success be defined statistically?
% Various methods already exist and various new ones have been proposed in
% response to the crisis. This thesis centres around a proposal based on the
% reverse-Bayes approach. The key idea is to reverse the traditional ``forward''
% use of Bayes' theorem (``prior + likelihood $\rightarrow$ posterior''),
% starting instead with a pre-specified posterior and deducing the corresponding
% prior (``posterior + likelihood $\rightarrow$
% prior''). % As such, the reverse-Bayes approach naturally fits to the replication
% % setting as it enables the mathematical formalization of scepticism regarding the
% % finding from the original study.
% This allows us to challenge the original finding by determining a sceptical
% prior for the underlying effect size such that the resulting posterior is no
% longer convincing. This prior then represents the position of a sceptic who
% remains unconvinced by the original study. Whether or not the sceptics'
% position is justified can then be assessed in light of the new data from the
% replication study. The larger the conflict between the replication data and
% the sceptic, the larger the degree of replication success. This procedure can
% be summarized in a single quantitative measure of replication success, termed
% the sceptical $p$-value.

### 2022-12-15 intro.Rnw
rewrite intro and abstract a bit

\begin{wrapfigure}{r}{0.29\textwidth}
  \centering
  \includegraphics[height = 6.9cm]{images/xkcdCrop.png}
  \caption*{Replication studies as \mbox{illustrated} by Randall Munroe
    \mbox{(\url{https://xkcd.com/242})}.}
\end{wrapfigure}

% How can we know if a finding from a scientific study is really true? For
% example, how can we know if the protective effect of a vaccine found in a study
% is real? The answer to such questions is of high importance to scientists,
% decision makers, and the general population. However, because any study result
% comes with uncertainty we can never know for sure.
How can we know whether we can trust a finding from a scientific study? For
example, how can we know whether the protective effect of a vaccine found in a
study is indeed existent or whether it is just a spurious finding? The answer to
such questions is of high importance to researchers, decision makers, and the
general population, and one way to address them scientifically is through
\emph{replication studies}.

A replication study consists of repeating the original study as closely as
possible but with new subjects. Such a study may yield similar results which
would make us more confident about the original finding, or may yield
conflicting results which would lower our confidence. As such, replication
studies are an essential part of the scientific method as they provide a means
for substantiating genuine research findings and refuting research findings
which occurred merely by chance. For this reason, ``successful'' replication is
often a requirement, for instance, for acceptance of newly proposed scientific
theories (\eg{} a new physical model) or the implementation of policies based on
scientific knowledge (\eg{} market approval of a drug). The results from
replication studies may hence have real world consequences, % , such as deciding
% whether we receive the recommendation to get vaccinated (a consequence that
% anyone who experienced the COVID-19 pandemic is very aware of)
and it is therefore important that methodological aspects of replication
studies, such as their statistical design and analysis, are well understood.

Despite their tremendous importance, the traditional academic system has made it
unattractive for researchers to conduct replication studies; the currencies of
science -- publications, citations, and grant money -- are typically easier to
acquire by conducting novel research. This is because until recently, most
scientific journals hardly published any replication studies as the emphasis was
on ``innovation'' rather than on ``repetition'' \citep{Makel2012, Martin2017,
  Coiera2021}. To build a successful career, researchers thus often had no other
choice than to concentrate their efforts on producing novel and eye-catching
research results \citep{Binswanger2014, Moher2018}.

>>>>

\begin{wrapfigure}{r}{0.27\textwidth}
  \centering
  \includegraphics[height = 6.9cm]{images/xkcdCrop.png}
  \caption*{Replication studies as \mbox{illustrated} by Randall Munroe
    \mbox{(\url{https://xkcd.com/242})}.}
\end{wrapfigure}

% How can we know if a finding from a scientific study is really true? For
% example, how can we know if the protective effect of a vaccine found in a study
% is real? The answer to such questions is of high importance to scientists,
% decision makers, and the general population. However, because any study result
% comes with uncertainty we can never know for sure.
The ability to trust scientific findings is essential for making evidence-based
decisions. But how can we know whether a scientific finding is trustworthy? For
instance, how can we know whether the protective effect of a vaccine found in a
study is indeed existent, or whether it is just a spurious finding? One way to
answer this question is through the use of \emph{replication studies}.

A replication study (or, simply, replication) involves repeating the original
study as closely as possible but with new subjects. If the replication yields
similar results to the original study, this increases our confidence in the
original finding. However, if the replication study yields conflicting results,
this lowers our confidence in the original finding. As such, replication studies
are an essential part of the scientific method. They provide a means for
substantiating genuine research findings and refuting findings which occurred
merely by chance. For this reason, ``successful'' replication is often a
requirement for acceptance of newly proposed scientific theories (\eg{} a new
physical model). Yet, replication studies are not only important for
researchers, but also for decision makers and the general population, as the
implementation of policies based on scientific findings may also depend on
whether these findings can be replicated (\eg{} market approval of a drug). The
results from replication studies may thus also have real-world consequences, and
it is therefore important that the methodological aspects of replication
studies, such as their statistical design and analysis, are well understood.

Despite their importance, the traditional academic system has made it
unattractive for researchers to conduct replication studies; the currencies of
science -- publications, citations, and grant money -- are typically easier to
acquire by conducting novel research. This is because until recently, most
scientific journals hardly published any replication studies as the emphasis was
on ``innovation'' rather than on ``repetition'' \citep{Makel2012, Martin2017,
  Coiera2021}. As a result, researchers often had no other choice than to focus
their efforts on producing novel and eye-catching research results in order to
build successful careers \citep{Binswanger2014, Moher2018}.
